---
title: Summarize NA's 
author: Ravi Chowdhury
date: '2021-04-01'
slug: summarize-na
categories:
  - post
tags:
  - dplyr
  - tidyverse
  - R
subtitle: 'Summarize NA''s across columns using dplyr (across) function'
summary: ''
authors: []
lastmod: '`r Sys.time()`'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, comment = "#")
library(tidyverse)
library(tidylog)
```

```{r, include=TRUE, echo=FALSE}
penguin <- palmerpenguins::penguins
```

## Exploring the table
We will use the palmerpenguins data from the `palmerpenguins` package.

```{r}
penguin %>% slice_head(n = 10)
```

`slice_head` is a function from `dplyr` package, that shows the top `n` rows in the dataset. In this case we are just looking at top 10 row.

Since `dplyr` version 1.0.0 there has been a new function `across`. This function basically allows you to apply a function across different columns. The `across` function is very powerful and it can be used in various way. For today we will just use this function to summarize missing values `NA` from our dataset. For more information about `across` click **[here](https://dplyr.tidyverse.org/reference/across.html)**

```{r}
penguin %>% 
  summarise(across(.cols = everything(), ~ sum(is.na(.))))
```
`.cols` is a `tidy-select` argument, so you can basically use it in multiple ways e.g based on location of column `3:5`
```{r}
penguin %>% 
  summarise(across(.cols = 3:5, ~ sum(is.na(.))))
```
or specify the column name
```{r}
penguin %>% 
  summarise(across(.cols = c(bill_length_mm, bill_depth_mm, flipper_length_mm), ~ sum(is.na(.))))
```
or matching name patterns like `ends_with("mm")`
```{r}
penguin %>% 
  summarise(across(.cols = ends_with("mm"), ~ sum(is.na(.))))
```
or you can also pass a character vector
```{r}
cols_to_pull <- c("bill_length_mm", "bill_depth_mm", "flipper_length_mm")
penguin %>% 
  summarise(across(.cols = all_of(cols_to_pull), ~ sum(is.na(.))))
```
These are some of the ways you can use the `.cols` argument. The `~` after that is basically the function that you want to apply to those columns. In this case we just want to `sum` all the `NA's` in the columns.






