---
title: 'Import Multiple SQL Tables in R '
author: Ravi Chowdhury
date: '2021-12-02'
slug: []
categories:
  - post
tags:
  - R
  - SQL
subtitle: ''
summary: 'Import SQL tables in R and export in Excel'
authors: []
lastmod: '2021-12-02T11:14:18-06:00'
featured: no
draft: no
disable_jquery: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, comment = "#")
library(tidyverse)
library(tidylog)
library(DBI)

```

#### In this post I will be using a function to import multiple tables from a SQL database. This is helpful in case you want to import multiple tables and export them to a flat file like .csv or .xlsx or if you want to import the files to R for anaylsis. In this example I will just be using it to import it into a nested data frame / tibble and then exporting them to a single flat file with multiple tabs.
#### I will be using the `tidyverse` and `dbi` packages.

```{r}

```

