---
title: Renaming columns
author: Ravi Chowdhury
date: '2021-04-08'
slug: renaming-columns
categories: []
tags: []
subtitle: ''
summary: 'Using rename function in dplyr'
authors: []
lastmod: '`r Sys.time()`'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, comment = "#")
library(tidyverse)
library(tidylog)
```

## For renaming columns  with  dplyr we can use the ` rename`  &  `rename_with`  function.


The `rename` function works as follows new_col = old_col_name where new_col is the new name for the existing column (old_col_name)

```{r, include=TRUE, echo=FALSE}
penguin <- palmerpenguins::penguins
```

## Exploring the table
We will use the palmerpenguins data from the `palmerpenguins` package.

```{r}
penguin %>% colnames()
```

For just simple renaming of columns use the `rename` function
```{r}
penguin %>% 
  rename(species_penguin = species) %>% 
  colnames()
```
We can also pass multiple columns 

```{r}
penguin %>% 
  rename(
    species_penguins = species,
    island_penguins = island,
    sex_penguin = sex
  ) %>% 
  colnames()
```
`rename_with` function in `dplyr` is a much more powerful function that can be used to rename columns by passing a function to it. You can pass the `.cols` argument as well as the `.fn` argument to this function. `.cols` is a `tidyselect` function which opens various way of selecting columns like `last_col`, `any_of`, `all_of`, `everything` , `c()`, `starts_with` etc and `.fn` is used to pass a function to it.

Renaming all columns to uppercase

```{r}
penguin %>% 
  rename_with(
    .fn = ~ toupper(.),
    .cols = everything()
  ) %>% 
  colnames()
```
Rename just the columns that end with "mm".
```{r}
penguin %>% 
  rename_with(
    .fn = ~ toupper(.),
    .cols = ends_with("mm")
  ) %>% 
  colnames()
```
Also we don't have to specify `.cols` and `.fn` argument, you can just pass the argument without specifying the, just make sure to maintain the order. The `.fn` argument followed by the `.cols` argument. 

```{r}
penguin %>% 
  rename_with(
    ~ toupper(.),
    ends_with("mm")
  ) %>% 
  colnames()
```
We can also use the wonderful `glue` package to add a prefix / suffix to the column names.
```{r}
penguin %>%
  rename_with(
    ~ glue::glue("{.}_penguin"),
    ends_with("mm")
  ) %>% 
  colnames()
```

These are some of the ways to rename columns using `rename` and `rename_with` function using `dplyr`. For more details about the function please visit the **[tidyverse](https://dplyr.tidyverse.org/reference/rename.html)**  website.







